\chapter*{\textbf{CONCLUSION}}
\thispagestyle{empty}
\numberwithin{equation}{chapter}

\par ~~~~~~~~The study of differential equation is a wide field in pure and applied mathematics,  physics and engineering. All these disciplines are concerned with the properties of differential equations of various types. Pure mathematics focuses on the existence and uniqueness of solutions, while applied mathematics emphasizes the rigorous justifications of the method for approximating solutions.

\par ~~~~~~~~~~This work illustrates the breadth and depth of the mathematical methods currently applied in medicine, specifically in oncology, cardiology, epidemiology, and pharmacokinetics. Nowadays mathematics is being successfully applied to a number of important fields in medicine including , cardiovascular diseases, clinical schedules and tests, drug design and discovery, epidemiology, genetics, and more. All this research has contributed to and continues to increasingly contribute both to better understand medical phenomena and to finding practical ways of action. It also illustrates nicely how different mathematical subject areas usually concur in the modelling and analysis of a specific topic.


\par ~~~~~~~~It is important to emphasize that none of these problem areas has been satisfactorily solved, and all of the algorithms we have described are open to considerable improvement. The first few chapter addresses aspects of growth and decay, especially biological growth of cell or organ etc. Later it deals with the topics in differential equations that covers dynamics of tumor growth, epidemiology,cardiovascular system response dynamics to exercise stress, detection of diabetes and finally drug distribution in the field of pharmacokinetic (single and double compartment systems) including absorption of drug in organs or cells.


\par ~~~~~~~~~~Ordinary differential equations (ODEs) provide a classical framework to model the dynamics of biological systems, given temporal experimental data. Qualitative analysis of the ODE model can lead to further biological insight and deeper understanding compared to traditional experiments alone. This short paper will provide an overview of the ODE modelling framework, and present examples of how ODEs can be used to address problems in medicine. Completion of this thesis, Differential equations in Medicine, as well as being able to solve first-order differential equations we should find that you are increasingly able to communicate mathematical ideas and apply your knowledge and understanding to mathematics in everyday life.



